\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}

\title{Development Plan\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Sept. 18, 2025 & Daniel Maurer & First draft of Workflow Plan\\
Sept. 19, 2025 & Olivia Reich & First draft of Sections 1-6\\
Sept. 19, 2025 & Daniel Maurer & First draft of POC Plan\\
Sept. 20, 2025 & Khalid Farag & Added group reflection\\
Sept. 20, 2025 & Daniel Maurer, Olivia Reich & Updates to respective sections based on reviews\\
Sept. 21, 2025 & Khalid Farag & First Draft of Project Decomposition and Scheduling\\
Sept. 21, 2025 & Andrew Bovbel & First Draft of Expected Technologies and Coding Standard\\
Sept. 21, 2025 & All & Team Charter\\
Sept. 22, 2025 & All & Final Revisions to respective sections\\
April 2nd, 2026 & Khalid Farag & Final Changes to Development Plan\\
\bottomrule
\end{tabularx}
\end{table}

\newpage{}

\iffalse
\wss{Put your introductory blurb here.  Often the blurb is a brief roadmap of
what is contained in the report.}

\wss{Additional information on the development plan can be found in the
\href{https://gitlab.cas.mcmaster.ca/courses/capstone/-/blob/main/Lectures/L02b_POCAndDevPlan/POCAndDevPlan.pdf?ref_type=heads}
{lecture slides}.}
\fi

The following document will provide an overview of the team plans for the project development process. It will
establish plans to promote effective collaboration throughout the entire project as well as define roles and
responsibilities to help guide successful team dynamics. It will provide insight into the plans for project
execution through a workflow plan that is supported by an outline of the methods that will successfully demonstrate
proof of concept as the project progresses. It also provides a high-level understanding of the technological
concepts that will be explored and adopted throughout the project.

\section{Confidential Information}

\iffalse
\wss{State whether your project has confidential information from industry, or
not.  If there is confidential information, point to the agreement you have in
place.}\\
\fi

At this time, there is no confidential information that is relevant to note within the current project scope.

\iffalse
\wss{For most teams this section will just state that there is no confidential
information to protect.}
\fi
\section{IP to Protect}

\iffalse
\wss{State whether there is IP to protect.  If there is, point to the agreement.
All students who are working on a project that requires an IP agreement are also
required to sign the ``Intellectual Property Guide Acknowledgement.''}
\fi

At this time, an IP is not relevant to the current project scope.

\section{Copyright License}

\iffalse
\wss{What copyright license is your team adopting.  Point to the license in your
repo.}
\fi

This project is licensed under the MIT License. See the \href{./LICENSE}{LICENSE} file for details.

\section{Team Meeting Plan}

\iffalse
\wss{How often will you meet? where?}

\wss{If the meeting is a physical location (not virtual), out of an abundance of
caution for safety reasons you shouldn't put the location online}

\wss{How often will you meet with your industry advisor?  when?  where?}

\wss{Will meetings be virtual?  At least some meetings should likely be
in-person.}

\wss{How will the meetings be structured?  There should be a chair for all meetings.  There should be an agenda for all meetings.}
\fi

This section includes information regarding meeting frequency, location, and structure, for both the team and with its supervisor.\\

A basic group standard will be the organization of a group meeting that occurs a minimum of at least once a week to
allow for discussion on current project progress and future planning. Given weekly variations in personal schedules, there
will not be a specific date and time that the group abides by each week. Instead, the individual who takes on the
role of the Meeting Chair will be in charge of organizing a date and time each week that best accommodates the
schedule of each person. The nature of the meeting, regarding whether it will be in-person or virtual, will be
established upon determining the date and time of the meeting. As a general principle, in-person meetings will be
favoured as they typically help facilitate deeper collaboration and build better relationships amongst team
members. All in-person meetings should be conducted on campus, unless a different location is agreed upon by the
group. If a group member is unable to attend a certain meeting, they should notify the group through the WhatsApp
group chat as soon as possible.\\

The individual who takes on the role of the Notetaker will document all parts of the meeting. Certain points of
discussion may be established prior to the meeting, either during a previous meeting or during the period leading
up to the meeting. The Notetaker will work with the Team Manager to establish an agenda of all discussion points
and deadline reminders prior to the meeting. This agenda will be documented in the meeting report. During the
meeting, the Meeting Chair will be responsible for ensuring all points of discussion are adequately covered. At the
end of the meeting, it is the responsbility of the Notetaker to ensure the meeting has been properly documented.
The meeting documentation expectations have been specified under the Notetaker description in Section 6.\\

Meetings with our supervisor, Dr. Onaizah, will be organized based on the need to provide more in-depth explanations
on the progress of the project or to facilitate a discussion if there are many questions in which Dr. Onaizah can
provide insight. There will be no set schedule for when these meetings will occur. Once the team establishes that a
meeting with Dr. Onaizah is required, the team will create a list of potential dates and times that they are able
to present as options for Dr. Onaizah. Unless the group decides to specifically request either an in-person or
online meeting to accommodate specific group needs, the nature of the meeting will be determined based on the
preference of Dr. Onaizah.

\section{Team Communication Plan}

\iffalse
\wss{Issues on GitHub should be part of your communication plan.}
\fi

This section details where, how, and what communication amongst the team will take place and look like.\\

All informal communication should be initiated through a WhatsApp group chat that has already been established. It
is the responsibility of all group members to ensure they have access to the group chat and are actively monitoring
all messages that occur through this channel of communication. The primary focus of this group chat is to facilitate
easy and quick communication regarding small issues and meeting organization.\\

Meetings should be a regular occurrence to establish consistent and clear communication that can’t be achieved
solely through text communication. As established within the Team Meeting Plan, there will be a standard weekly scheduled
team meeting. If a discussion that starts through the group chat seems to require additional time, effort, or
broader input to consider different perspectives, the discussion may be postponed until it is able to be discussed
during a meeting. This means that it can either be noted as an official point of discussion within the weekly
scheduled team meeting or a separate meeting may be scheduled depending on the urgency of the discussion.\\

The creation of issues in the GitHub team repository will be the primary way to formally document all plans,
discussions and deadlines that have been discussed. All notable information that should be known by all group
members must be documented as a GitHub issue. Even if information has been stated in a different communication channel,
such as a group chat or team meeting, it must still be documented in GitHub to provide consistency and ensure there
are no oversights.\\

In the event that any communication occurs outside the WhatsApp group chat or a team meeting, it must still be
noted in the GitHub team repository. Individuals should do their best to not stray from the standard communication
channels unless extenuating circumstances apply or an additional standard communication channel has been established
by the group throughout the project progression. This will help ensure there is consistency in communication amongst
the entire group.\\

At a minimum, the team will provide the supervisor, Dr. Onaizah, with updates at least bi-weekly. Prior to providing
an update for Dr. Onaizah, the team will establish whether a meeting with her is necessary within the next week.
Meetings with Dr. Onaizah will be organized as needed. Key stakeholders will be handled in a similar manner. This
includes the grad student, Kaitlyn Clancy, that created the 3D printer and works directly under Dr. Onaizah. If relevant, Kaitlyn 
may be cc’d onto email updates to Dr. Onaizah or separate meetings may be organized.

\section{Team Member Roles}

\iffalse
\wss{You should identify the types of roles you anticipate, like notetaker,
leader, meeting chair, reviewer.  Assigning specific people to those roles is
not necessary at this stage.  In a student team the role of the individuals will
likely change throughout the year.}
\fi

The following table outlines the initial role assignments for each team member at the start of the project.
Roles may rotate or shift throughout the year as the project evolves and according to the situation.
Multiple members may take on the same role (e.g.\ in the case of Domain Expert and Code Reviewer).\\

Current role assignments were determined based on both individual interests and the strengths each team member identified during discussions. It has been established within the team that all members are expected to reflect individually on their performance in fulfilling their assigned roles as well as on the contributions of their teammates after each milestone. Transitioning team members to different roles will only occur if one of the following circumstances occurs:

\begin{enumerate}
  \renewcommand{\labelenumi}{(\arabic{enumi})}
  \item A team member expresses interest in trying a new role.
  \item A team member feels that another team member is underperforming and has not sufficiently fulfilled the responsibilities of their role.
\end{enumerate}

If either of the above two events occurs, the protocol is that the team will plan out a specific meeting to reassess individual responsibilities and determine how roles should be redistributed.\\

The following table outlines the initial role assignments for each team member at the start of the project.

\begin{center}
\begin{tabularx}{\textwidth}{lX}
  \toprule
  \textbf{Role} & \textbf{Team Member(s)} \\
  \midrule
  Team Manager        & Omar Hassan Adelhamid \\
  Notetaker           & Daniel Maurer \\
  Meeting Chair       & Daniel Maurer \\
  Document Reviewer   & Khalid Farag \\
  Code Reviewer       & Andrew Bovbel, Olivia Reich, Daniel Maurer \\
  Communication Officer & Omar Hassan Adelhamid \\
  Domain Expert       & Khalid Farag, Olivia Reich, Andrew Bovbel \\
  \bottomrule
\end{tabularx}
\end{center}

The following are descriptions of each role that team members will take on throughout the year.\\

\textit{Team Manager} - The individual who takes on this role will take the lead on keeping the team on track. They
will closely monitor the deadlines and ensure that the team is on track with meeting the course deadlines as well as
the group deadlines that have been agreed upon ahead of time.\\

\textit{Notetaker} - During meetings, this individual will be responsible for keeping track of what was discussed
and who attended the meetings. They will also be required to create a report, in the form of a GitHub issue, that is accessible to each group member
at the end of a meeting. This report will include a summary of what was discussed, a meeting agenda for what has to
be discussed, a review of what has changed since the previous meeting, a list of key tasks to complete prior to the
next meeting and an outline of deadlines that are relevant at the current stage of the project.\\

\textit{Meeting Chair} - This individual will be responsible for organizing meetings and ensuring that the team is
following the Team Meeting Plan as specified above. They will ensure that the team is meeting at a sufficient
frequency to facilitate effective collaboration both within the group and with Dr. Onaizah. They will also take
the lead on team discussions regarding future meetings and do their best to reasonably accommodate the schedule of
all team members when determining a date and time.\\

\textit{Document Reviewer} - This individual will take on the responsibility of monitoring the review of all
documents. They will ensure that team deadlines provide reasonable buffer for review prior to the official course
due date. They will organize who reviews each section of the relevant documents being submitted as well as complete
an overall final review prior to submission. This final review should include verifying the consistency,
formatting, and grammar of the document. They will also work closely with the code reviewer to ensure the code and
documentation properly align.\\

\textit{Code Reviewer} - This individual will have similar responsibilities to the document reviewer but will focus
on reviewing the code. This includes monitoring the integration of individual code contributions during each
iteration in the development stage. They will organize milestone code check-ins to ensure that after major code
contributions the functionality of previous code has not been compromised in any way and still runs seamlessly. They
will also work closely with the document reviewer to ensure the code and documentation properly align.\\

\textit{Communication Officer} - The individual who takes on this role will be responsible for handling the majority
of the communication with our supervisor and key stakeholders. Specific communication responsibilities include
sending emails when relevant, closely monitoring their email for replies, keeping all relevant parties in the loop
regarding the progress of the project, and conveying important information from these emails to the rest of the team
members.\\

\textit{Domain Expert} - This individual will be considered the de facto expert on a given area of knowledge (eg. 
3D rendering libraries, 3D printing) and will be responsible for conducting research to disseminate to the group, answering questions
from other members about subject matter, and either assisting or taking the lead role in technical aspects relating to 
their subject. They will be a key informant in team meetings, and will work closely with the code and document reviewers
to assist in any technical review related to their subject matter of expertise.

\section{Workflow Plan}

\iffalse
\begin{itemize}
	\item How will you be using git, including branches, pull request, etc.?
	\item How will you be managing issues, including template issues, issue
	classification, etc.?
  \item Use of CI/CD
\end{itemize}
\fi

This section details how Git will be used throughout the project, as well as how Continuous Integration/Deployment will be implemented. Git will be utilized as the primary, centralized collaboration space for both project
source code and its related documentation. The GitHub repository can be found at \href{hub.com/OmarHassanAdelhamid/Five-of-a-Kind-capstone-project-/}{GitHub Repository}. The repository will maintain one permanent protected branch:

\begin{itemize}
  \item \texttt{main} --- the stable branch representing the latest submitted or
  release-ready state of the project. Direct pushes are not permitted; all changes
  must arrive via a reviewed pull request from a short-lived branch.
\end{itemize}

All other branches are short-lived and must follow the naming convention
\texttt{<name>-<description>}, where \texttt{name} is the author's first name and
\texttt{description} is a brief \texttt{kebab-case} summary of the work (2--4 words).
Branches will not be shared between members; each member creates their own branch
for each unit of work. For example, a branch by Khalid to implement voxel rendering
would be named \texttt{khalid-voxel-rendering}. Once the work on a branch is complete
and its pull request is merged into \texttt{main}, the branch should be deleted.\\

Commits should each contain a descriptive message of all edits, and ideally not lump together various changes.
When a member is complete with their work on a given branch, they will create a pull request
with an appropriate description describing changes, related labels, and reviewers.
For instance, an acceptable reviewer could be someone working on a related feature,
or the group if it affects everyone. Labels should give an estimate of how long it might take to
review. Each pull request should also be linked to a given issue (eg.\ via \texttt{closes \#20}). Comments within pull
requests will also be taken advantage of, allowing feedback to be directly linked to source
code or documentation.

A milestone will be created for each deliverable (both documentation and revisions) and issues
created will be associated with it. Issue templates will be used in the following ways:

\begin{itemize}
  \item lecture - to track attendance as well as general notes/questions
  \item meeting(s) - to record meeting minutes, attendance, and catch up members that miss the meeting
  \item peer revie - to request another team review a given section
\end{itemize}

Additionally, all issues will be categorized under a specific label to ensure clear organization and efficient tracking. The following are examples of general labels expected to be used:

\begin{itemize}
  \item documentation - tasks and document components involved in the creation of new documents.
  \item reflection - tasks related to reflection components within a document
  \item bug - known bugs in the code that must be resolved
  \item enhancement - features in the code that currently meet basic functional requirements but require further refinement to enhance performance, usability, or reliability
  \item lecture - upcoming lecture that all team members are required to attend
  \item meeting - upcoming scheduled meeting that all team members are required to attend
\end{itemize}

For larger tasks, specific labels will be created to allow for quick searching through issues.

All issues should also contain a reasonable description describing the bug/feature/section of documentation.
As a rule of thumb, issues should not be the full task but rather manageable, assignable chunks of it (eg. Finish Requirements Doc is a bad issue; Finish a specific section of the Doc would be better). Similar to pull requests, issues will also be given assignees, who will also be responsible for managing issue movement in the GitHub project (eg. moving from In Progress to In Review).

To incorporate continuous integration, upon each push/pull request, all tests in the test suite will be run automatically via GitHub Actions.

\section{Project Decomposition and Scheduling}

\iffalse
\begin{itemize}
  \item How will you be using GitHub projects?
  \item Include a link to your GitHub project
\end{itemize}

\wss{How will the project be scheduled?  This is the big picture schedule, not
details. You will need to reproduce information that is in the course outline
for deadlines.}
\fi

This section details how the project will be decomposed into manageable pieces and how these parts are scheduled.\\

The team will use GitHub Projects as the central platform to monitor the progress of the project. This tool will help ensure that issues/tasks are organized, responsibilities are clear, and the project is on track. The link to the GitHub project is here: \href{https://github.com/users/OmarHassanAdelhamid/projects/2/views/1}{GitHub Project}.

\subsection{GitHub Projects}

GitHub Projects will be used to plan, manage, and track the workflow by creating issues and
organizing them through the different stages of the project. The project board will use the
following columns, through which every issue must progress in order:

\begin{center}
\begin{tabularx}{\textwidth}{lX}
  \toprule
  \textbf{Column} & \textbf{Description} \\
  \midrule
  Backlog     & All identified tasks that have not yet been scheduled for the current
                iteration. Issues are created here first. \\
  In Progress & Tasks actively being worked on. An issue should move here when a
                corresponding branch is created. \\
  In Review   & Tasks whose pull request has been opened and is awaiting code or
                document review. \\
  Done        & Tasks whose pull request has been approved and merged. \\
  Meetings    & Meetings that have been scheduled either between the team or with the supervisor and are recorded in the GitHub project. \\
  Lectures    & Lectures that have been attended and are recorded in the GitHub project. \\
  \bottomrule
\end{tabularx}
\end{center}

\subsection{Project Scheduling}

The project will be scheduled based on the capstone deliverables, the team will prioritize the deliverables and schedule them accordingly. At each deliverable, the work will be decomposed and assigned to team members, then tracked through GitHub Projects until completion. Below is a table of the project deliverables and their corresponding due dates.

\subsubsection*{Task Decomposition Strategy}

Tasks will be decomposed differently depending on the nature of the deliverable:

\begin{itemize}
  \item \textbf{Documentation deliverables} will be broken down by section or subsection, ensuring each piece is small enough to review and merge independently.
  \item \textbf{Software deliverables} will be broken down by feature or module, so that each GitHub issue maps to a well-scoped, independently testable unit of work.
\end{itemize}

\subsubsection*{Task Distribution and Skill Development}

Tasks will be distributed among team members with two competing goals in mind: leveraging existing strengths to maintain quality, and making sure each team member gets to work on a variety of tasks. Assigning the same individual to the same type of task throughout the entire project risks leaving other members without a working understanding of critical system components. To address this:

\begin{itemize}
  \item \textbf{Pairing will be used for high-complexity or unfamiliar tasks.} When a team member is assigned a task outside their current skillset, they will be paired with a domain expert who can provide guidance without owning the work outright.
  \item \textbf{Task assignments will be made collectively during team meetings} so that all members have visibility into who is doing what, and can flag any issues early.
\end{itemize}

\subsubsection*{Ensuring Task Completion}

To reduce the risk of assigned tasks going incomplete or being rushed at the last minute, the team will adopt the following practices:

\begin{itemize}
  \item \textbf{Internal deadlines} will be set at least two to three days before each official course deadline, providing buffer for issues and reviews.
  \item \textbf{Check-ins} will be held during the weekly team meeting to bring up any blockers on in-progress issues before they become critical.
  \item \textbf{If a team member anticipates missing an internal deadline}, they are expected to communicate this as early as possible in the team chat so that the task can be re-assigned or supported by another member.
\end{itemize}

\subsubsection*{Project Deliverables and Due Dates}
Below is a table of the project deliverables and their corresponding due dates.

\begin{center}
  \begin{tabularx}{\textwidth}{Xc}
    \toprule
    \textbf{Deliverable} & \textbf{Due Date} \\
    \midrule
    Problem Statement, Proof of Concept, and Development Plan &
    September 22th, 2025 \\
    SRS and Hazard Analysis Revision 0 & October 6th, 2025 \\
    V\&V Plan Revision 0 & October 27th, 2025 \\
    Design Document Revision 1 & November 10th, 2025 \\
    Proof of Concept Demonstration & November 17th, 2025 - Nov 26th, 2025 \\
    Design Document Revision 0 & January 19th, 2026 \\
    Revision 0 Demonstration & February 2nd, 2026 - Feb 11th, 2026 \\
    V\&V Report and Extras Revision 0 & March 9th, 2026 \\
    Final Demonstration (Revision 1) & March 23rd, 2026 - March 26th, 2026 \\
    Final Documentation (Revision 1) & April 6th, 2026 \\
    EXPO Demonstration & TBD \\
    \bottomrule
  \end{tabularx}
\end{center}




\section{Proof of Concept Demonstration Plan}

\iffalse
What is the main risk, or risks, for the success of your project?  What will you
demonstrate during your proof of concept demonstration to convince yourself that
you will be able to overcome this risk?
\fi

This section details what will constitute the project's initial proof of concept, and explain 
how the demonstration mitigates potential risks.\\

Our POC Demonstration Plan will begin with a pre-existing CAD file. Taking this 
CAD file, we will then:

\begin{enumerate}
  \item \textbf{Show the process of importing the file into our software.} This would include converting the file properly and showing the key feature of `slicing' the model into voxels.
  \item \textbf{Demonstrate that the software can load and render simple voxel models.} A simple render of a small model will be shown of both the CAD file and the voxelised output. Magnetization of voxels will be left out of this demo.
  \item \textbf{Show the process of exporting the file into a standard format.} This includes converting the project file successfully into a format deemed acceptable by the existing 3D printing software.
\end{enumerate}

There are two primary risks associated with this demo:

\begin{enumerate}
  \item \textbf{Unfamiliarity with dependencies may result in difficuties with file conversion.} As time worked on the project increases, so will familiarity, but for the proof of concept, group members will be largely unfamiliar with both libraries needed to work with CAD files and Dr. Onaizah’s current codebase.
  \begin{itemize}
    \item[] \textit{Relevant Risk Mitigation Considerations:} If there is difficulty converting the file due to limited knowledge of the required dependencies, the group will need to reassess how CAD files are processed within the system. This may require additional time spent understanding and experimenting with the libraries used for CAD file handling as well as further analysis of Dr. Onaizah’s existing codebase. The team may also need to review relevant documents and seek out existing examples to deepen our knowledge of the file conversion process. For the demo, the primary objective will be to demonstrate that a simple CAD file can be successfully converted, validating the core functionality of the pipeline. 
  \end{itemize}
  \item \textbf{File converting time is longer than converting the model manually.} While stakeholders have stated that process automation is the ultimate goal, the fact remains that our software should be reasonably more efficient than the current solution, which requires rebuilding the model by hand.
  \begin{itemize}
    \item[] \textit{Relevant Risk Mitigation Considerations:} If the software that is built does not provide a more efficient process, our group will need to reanalyze how the files are converted from the CAD file into our software. This may require further investigation into different methods of handling the initial files that will potentially speed up the process. This may include strategies such as optimizing mesh before conversion, using more efficient file formats, parallelizing the voxelization process, or optimizing how files are loaded and parsed. It may also require reconsidering if the scope regarding voxel customizability should be paired back for initial iterations. For the demo, we plan to show that a simple CAD file can be converted in a similarly short amount of time.
  \end{itemize}

\end{enumerate}


A secondary risk is that rendering the model in 3D may be slow. Initial iterations may be laggy 
due to lack of group experience with 3D rendering. High memory usage may result from 
inefficient handling of large voxel grids, reducing responsiveness. Should this be 
the case, the group will need to revisit optimization strategies to find ways of 
improving memory usage and responsiveness. For the proof of concept, we will focus on 
rendering a smaller model as a first step in the process.

\section{Expected Technology}

\iffalse
\wss{What programming language or languages do you expect to use?  What external
libraries?  What frameworks?  What technologies.  Are there major components of
the implementation that you expect you will implement, despite the existence of
libraries that provide the required functionality.  For projects with machine
learning, will you use pre-trained models, or be training your own model?  }

\wss{The implementation decisions can, and likely will, change over the course
of the project.  The initial documentation should be written in an abstract way;
it should be agnostic of the implementation choices, unless the implementation
choices are project constraints.  However, recording our initial thoughts on
implementation helps understand the challenge level and feasibility of a
project.  It may also help with early identification of areas where project
members will need to augment their training.}

Topics to discuss include the following:

\begin{itemize}
\item Specific programming language
\item Specific libraries
\item Pre-trained models
\item Specific linter tool (if appropriate)
\item Specific unit testing framework
\item Investigation of code coverage measuring tools
\item Specific plans for Continuous Integration (CI), or an explanation that CI
  is not being done
\item Specific performance measuring tools (like Valgrind), if
  appropriate
\item Tools you will likely be using?
\end{itemize}

\wss{git, GitHub and GitHub projects should be part of your technology.}
\fi

This section details what technologies are expected to be utilized in the project; it is subject
to change as the project progresses and difficulties are found.\\

\subsection{Languages}

\textbf{\textit{TypeScript (with React) — For Frontend Development}}
\begin{itemize}
  \item React is a widely used and well-developed library that enables the development of responsive, modular, and component-based user interfaces.
  \item TypeScript enhances code maintainability through type safety and improved error detection compared to JavaScript.
  \item These features are especially important as the system is expected to evolve alongside the magnetic 3D printer, requiring a scalable and maintainable code.
\end{itemize}

\textbf{\textit{Python — For Backend Development}}
\begin{itemize}
  \item Python integrates well with frameworks such as FastAPI, allowing for efficient development of RESTful APIs.
  \item The language provides strong support for scientific and computational libraries, which are beneficial for handling voxel data and model processing.
  \item Python is widely used in the industry, which makes it a practical and easy choice for development and future expansion. It is also a well-known language within our group.
\end{itemize}

\subsection{External Libraries}

To support complex functionality, the team will leverage the following external libraries:\\

\textbf{\textit{Three.js — For 3D Visualization Implementation}}
\begin{itemize}
  \item It is one of the most widely used libraries for real-time web-based 3D graphics.
  \item It integrates well with React, making it suitable for building interactive voxel-based visualizations.
\end{itemize}

\textbf{\textit{Redux Toolkit — For State Management}}
\begin{itemize}
  \item It enables predictable and scalable management of application state.
  \item As the interface becomes more complex, it simplifies state management compared to relying solely on local component state.
\end{itemize}

\textbf{\textit{FastAPI — For Backend Framework}}
\begin{itemize}
  \item It allows backend REST endpoints to be built for validating and normalizing voxel data within the system.
  \item It provides high performance and automatic API documentation.
  \item It integrates well with Python-based data processing workflows.
\end{itemize}

\subsection{Data Storage}

\textbf{\textit{PostgreSQL — Local Instance, For Structured Storage}}
\begin{itemize}
  \item It supports relational data models, making it well-suited for storing voxel geometries and associated metadata.
  \item It provides strong querying capabilities and data consistency compared to file-based storage approaches, which is important for handling large datasets derived from high voxel counts.
  \item It allows for future scalability if the system expands beyond local usage.
\end{itemize}

\subsection{Linter Tools \& Unit Testing}

For code quality, the frontend will adopt \textbf{ESLint} as a linter, with \textbf{Jest} for unit and integration testing. The backend will rely on \textbf{pytest} for automated testing, with a tentative coverage goal of approximately 80\%. Code coverage reporting will be handled using tools such as \textbf{Istanbul}. These tools were selected because several members of the team are familiar with them and they are compatible with the chosen frontend and backend technologies.

\subsection{Version Control and Project Management}

Version control and project management will be conducted using \textbf{git}, \textbf{GitHub}, and \textbf{GitHub Projects}, which will serve as the central platforms for collaboration, task tracking, and issue management. Continuous integration will be implemented using \textbf{GitHub Actions}, with automated checks for linting, tests, and coverage included in the pipeline. These were chosen due to the team’s familiarity with them.


\section{Coding Standard}

\iffalse
\wss{What coding standard will you adopt?}
\fi
This section details complementary coding standards that will be enforced in this project, 
aligning with the expected technologies listed above.\\

\subsection{Coding Standards and Guidelines}

To ensure consistency, maintainability, and readability, the project will adopt
established coding standards for all areas of development.

For the \textbf{frontend} (TypeScript/React):
\begin{itemize}

\item Variable and function names will use \textbf{camelCase}, while
  \textbf{PascalCase} will be used for React components.
  \item The principle of \textbf{DRY} (Don’t Repeat Yourself) will guide code
  organization, promoting modular components and reusable utility functions.
  \item File and folder structures will be organized in a consistent
  \textbf{kebab-case} format for directories and filenames.
\end{itemize}

For the \textbf{backend} (Python/FastAPI):
\begin{itemize}
  \item Code will follow the \textbf{PEP~8} style guide
  \item Variable and function names will use \textbf{snake\_case}, while classes
  will be written in \textbf{PascalCase}.
\end{itemize}

Across both frontend and backend:
\begin{itemize}
  \item All code will be documented through inline comments and docstrings,
  particularly for APIs.
  \item \textbf{Unit tests} will accompany critical modules, following a goal of
  80\% code coverage.
  \item Commit messages will be written clearly and consistently, referencing
  related issues when applicable.
  \item Team members will adhere to software engineering principles such as
  \textbf{single responsibility}, \textbf{modularity}, and \textbf{clarity over
  cleverness}.
\end{itemize}

These conventions aim to produce code that is readable, maintainable, and
collaborative.

\subsection{Coding Standards Implementation Strategy}

To ensure the coding standards are enforced, the team has chosen to integrate the following practices into the development workflow:

\begin{itemize}
  \item \textbf{All code changes must be submitted through a pull request}, allowing for review and explicit approval from at least one other team member before being merged into the main branch.
  \item \textbf{At least one designated Code Reviewer} (as specified in Section 6, Team Member Roles) \textbf{must approve the pull request prior to merging}. In particular, this will include verification of the following:
  \begin{itemize}
      \item adherence to established naming conventions and project structure (e.g., camelCase/PascalCase for frontend and snake\_case/PascalCase for backend)
      \item adherence to DRY principles
  \end{itemize}
  \item \textbf{All commit messages must clearly describe the changes made}, including relevant context and references to associated issues when applicable.
  \item \textbf{Unit tests must be included for critical functionality.}
  \item \textbf{All pull requests must pass CI checks}, including successful test execution and linting, prior to approval and merge.
\end{itemize}

\newpage{}

\section*{Appendix --- Reflection}

\iffalse
\wss{Not required for CAS 741}
\fi
\input{../Reflection.tex}

\subsection*{1. Why is it important to create a development plan prior to starting the project?}
Creating a development plan prior to starting a project is essential because it provides a clear, structured roadmap for the team to follow, ensuring that all members are on the same page regarding the project's scope and requirements. This well-structured plan helps identify any potential risks or challenges early on, making it easier to address them before they become major issues. Overall, a development plan helps reduce uncertainty and improves overall efficiency by having a clear plan to follow.

\subsection*{2. In your opinion, what are the advantages and disadvantages of using CI/CD?}
In our opinion, the main advantage of using CI/CD when working on a project is that enables faster and more reliable development by automating builds, testing, and deployments. As a team, this helps us to catch any issues early on in the development process, and maintain a high quality of code. However, a disadvantage of CI/CD is that it requires a more complex setup and configuration, which can be time-consuming and require additional resources. In most cases, it is worth implementing CI/CD to improve the efficiency and quality of the development process.

\subsection*{3. What disagreements did your group have in this deliverable, if any, and how did you resolve them?}
In this deliverable, the group did not have any disagreements. We were able to complete the deliverable in a timely manner and with a high quality of work.

\newpage{}

\section*{Appendix --- Team Charter}

\iffalse
\wss{borrows from
\href{https://engineering.up.edu/industry_partnerships/files/team-charter.pdf}
{University of Portland Team Charter}}
\fi

\subsection*{External Goals}

\iffalse
\wss{What are your team's external goals for this project? These are not the
goals related to the functionality or quality fo the project.  These are the
goals on what the team wishes to achieve with the project.  Potential goals are
to win a prize at the Capstone EXPO, or to have something to talk about in
interviews, or to get an A+, etc.}
\fi

Besides our overall goal of achieving an A+ for this project, as a group we hope to 
contribute to a final product that genuinely assists Dr. Onaizah and her team in their 
studies and is potentially useful outside of this context. Additionally, we aim to build 
a project of sufficient quality to strengthen each team member's portfolio and increase 
their appeal to recruiters and future employers.

\subsection*{Attendance}

\subsubsection*{Expectations}

\iffalse
\wss{What are your team's expectations regarding meeting attendance (being on
time, leaving early, missing meetings, etc.)?}
\fi

Our group expects each member to attend as many meetings as they can, being on time 
or early if possible, and staying until all discussion points are satisfied. Any 
absences from meetings are expected to be brought up at the time of meeting arrangement 
or as soon as the member is aware of the absence. Any member repeatedly missing meetings 
will be dealt with through group discussion, aiming to find a solution that works for all members.

\subsubsection*{Acceptable Excuse}

\iffalse
\wss{What constitutes an acceptable excuse for missing a meeting or a deadline?
What types of excuses will not be considered acceptable?}
\fi

All members are aware that we each have busy schedules. That being said, these 
schedules should not interfere with deadlines; other members will not repeatedly 
do the work of another member due to a busy schedule. Personal emergencies or illness 
are valid excuses. Similarly, missing meetings due to professional obligations (eg. 
TA-ing a course) is valid. Forgetting, or using a busy schedule as a repeated excuse, is not.

\subsubsection*{In Case of Emergency}

\iffalse
\wss{What process will team members follow if they have an emergency and cannot
attend a team meeting or complete their individual work promised for a team
deliverable?}
\fi

Should an aforementioned emergency occur, the grouop member will let the team know as 
soon as possible on WhatsApp to allow the rest of the group to swiftly redistribute 
their work, or reschedule.

\subsection*{Accountability and Teamwork}

\subsubsection*{Quality}

\iffalse
\wss{What are your team's expectations regarding the quality
of team members' preparation for team meetings and the quality of the
deliverables that members bring to the team?}
\fi

Expectations have been established with our group regarding the quality and effort put forth for any meetings or any
milestone-related documents and work.\\

Specific expectations related to meetings are as follows:
\begin{itemize}
    \item Team members are responsible for reviewing the meeting agenda prior to the meeting and arriving prepared
    with a proper understanding of the current deliverable as well as what is to be discussed during the meeting.
    \item Team members should be ready with designated work completed in accordance with the agreed-upon deadlines.
    \item During the meeting, team members should be prepared to make meaningful contributions by providing updates
    on their progress, explaining the current status of their designated work and seeking guidance from the group
    regarding any  difficulties that may have come up.
\end{itemize}

Specific expectations related to milestone-related documents:
\begin{itemize}
    \item All deliverables should align with the group’s agreed-upon standards, demonstrating consistency, clarity,
    insightful thoughts and meticulous attention to detail throughout the entire document.
    \item In the event of any difficulties or challenges, an individual is required to bring this to the attention
    of their group members as soon as possible to ensure a resolution is able to be achieved and deadlines are still able to be met.
    \item Deadlines will be created for each deliverable with sufficient time for review and group members will be
    required to complete their designated work to the best of their abilities by these deadlines.
\end{itemize}

Specific expectations related to review and revisions:
\begin{itemize}
    \item Everyone is required to contribute in reviewing the work of their team members to ensure consistency among
    all documents.
    \item All revisions should be carefully completed to ensure no deliverable section is overlooked and all
    sections meet the quality standards set by the group.
    \item Unless extenuating circumstances apply, all revisions should be provided a minimum of 2-3 days before the
    deliverable deadline to ensure sufficient time for an individual to be able to apply the changes to their document.
\end{itemize}

\subsubsection*{Attitude}
Our team recognizes that maintaining the right attitude is essential for
building a positive, collaborative, and productive environment. We commit to
the following guiding principles:

\begin{itemize}
    \item \textbf{Respectful Communication:} Team members will listen to each
    other’s ideas with an open mind and provide constructive feedback.
    Discussions should remain on point and respectful of other people's time.

    \item \textbf{Accountability:} Each member accepts responsibility for their
    assigned tasks and is expected to meet agreed on deadlines. When
    challenges arise, members will communicate early and seek support from other members.

    \item \textbf{Positive Mindset:} We strive to maintain optimism and
    encouragement to help sustain team morale and motivation.

    \item \textbf{Commitment to Quality:} Every member will contribute their
    best effort to ensure the project meets high standards and reflects the
    collective dedication of the team.

    \item \textbf{Collaboration and Openness:} All members are encouraged to
    share their perspectives freely and work together to achieve shared goals.
\end{itemize}

By adopting these attitudes, our team aims to foster a culture of trust,
respect, and excellence that will support both the success of the project and
the growth of each member.

\iffalse
\wss{What are your team's expectations regarding team members' ideas,
interactions with the team, cooperation, attitudes, and anything else regarding
team member contributions?  Do you want to introduce a code of conduct?  Do you
want a conflict resolution plan?  Can adopt existing codes of conduct.}
\fi

\subsubsection*{Stay on Track}

\iffalse
\wss{What methods will be used to keep the team on track? How will your team
ensure that members contribute as expected to the team and that the team
performs as expected? How will your team reward members who do well and manage
members whose performance is below expectations?  What are the consequences for
someone not contributing their fair share?}

\wss{You may wish to use the project management metrics collected for the TA and
instructor for this.}

\wss{You can set target metrics for attendance, commits, etc.  What are the
consequences if someone doesn't hit their targets?  Do they need to bring the
coffee to the next team meeting?  Does the team need to make an appointment with
their TA, or the instructor?  Are there incentives for reaching targets early?}
\fi

To stay on track as a team, we will follow these necessary methods:

\begin{enumerate}
  \item \textbf{Regular Team Meetings:} We will hold meetings at least once a week to discuss progress, address any issues, and plan for the next deliverable. This meeting will be communicated through the team chat \textit{WhatsApp}. This meeting will be attended by all team members, unless otherwise specified.
  \item \textbf{Task Management:} We will use GitHub Projects to assign tasks, track progress, and ensure everyone is contributing their fair share. This is crucial to ensure that all team members contribute their fair share to the project.
  \item \textbf{Regular Updates:} We will update the supervisor and stakeholders regularly to keep them informed about our progress. This will be done through emails to the supervisor and the stakeholders. The supervisor will be updated at least once every two weeks, unless any questions arise.
\end{enumerate}

For team contribution and performance, we will follow these methods:

\begin{enumerate}
  \item \textbf{Attendance:} We will use GitHub Projects to track the attendance of each team member for team meetings, lectures and supervisor meetings. This is important to ensure that all team members are contributing their fair share to the project.
  \item \textbf{Contributions:} We will use GitHub Projects to track the contributions of each team member to the project. Each team member will be responsible for contributing to this capstone project to the best of their ability. Issues will be evaluated based on the quality of the work, the deadline and the effort put into the issue.
  \item \textbf{Code Review:} Each team member will be responsible for reviewing the code of the other team members to ensure that the work is completed at a high quality and on time. Each pull request will be reviewed by at least two other team members before it is merged into the main branch.
  \item \textbf{Performance Metrics:} We will use commits, meetings attended, and issues completed to evaluate the performance of each team member.
\end{enumerate}

For the rewards and consequences, we will follow these methods:

\begin{enumerate}
  \item \textbf{Rewards:} To reward members who do well and to encourage good performance, we will recognize their contributions and celebrate their achievements. They will have the option to decide which task they would like to work on for the next deliverable.
  \item \textbf{Managing underperformers:} We will consider a team member to be underperforming if they are not contributing to the project or are not meeting deadlines. To manage this, we will have a team meeting discussing the issue and offering support and guidance to the team member. If the issue persists, the team member will need to contribute to more tasks to make up for the work of the other team members.
\end{enumerate}


\subsubsection*{Team Building}
\iffalse
\wss{How will you build team cohesion (fun time, group rituals, etc.)? }
\fi

The team will make an effort to build team cohesion through the following methods: having post delivables hangouts to celebrate the small wins of crossing milestones. Have biweekly hangouts to catch up on non-project related topics while getting a snack or ice cream etc.

\subsubsection*{Decision Making} 

\iffalse
\wss{How will you make decisions in your group? Consensus?  Vote? How will you
handle disagreements? }
\fi

As a group, we believe the best way to make decisions is through concensus and discussion, 
as this ensures all members are satisfied with decision outcomes. However should the case 
arise that concensus cannot be reached, a vote will be held between conflicting parties.

Should a major disagreement result from one of these decisions, during the next meeting 
the team will focus on resolving it, with the main goal to get the entire group back on 
the same page and put personal feelings aside. Ultimately, the group shares the same goals 
and in these situations, that is what should be kept in mind. Should a resolution not be found, 
whichever goal is most related to the issue should be brought up as a reminder to all 
parties and a logical decision between options will be made with the goal central to discussion.

\end{document}
