\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev0 are
NOT included.

\section{Team Meeting Attendance}
\iffalse
\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}
\fi

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 11\\
Omar & 11\\
Daniel & 11\\
Andrew & 8\\
Olivia & 11\\
Khalid & 11\\
\bottomrule
\end{tabular}
\end{table}

We try to schedule meetings so that all can attend; if a team member missed meetings, it was discussed beforehand.

\section{Supervisor/Stakeholder Meeting Attendance}
\iffalse
\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}
\fi
\noindent \textbf{Supervisor's Name: } [Dr. Onaizah]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Omar & 2\\
Daniel & 3\\
Andrew & 2\\
Olivia & 2\\
Khalid & 1\\
\bottomrule
\end{tabular}
\end{table}

One of these meetings was with Dr. Onaizah's graduate student, Kaitlyn Clancy, who has acted as our secondary client.

\section{Lecture Attendance}
\iffalse
\wss{For each team member how many lectures have they attended over the time
period of interest.  This number should be determined from the lecture issues in
the team's repo. You can find the number of lectures in the time period of
interest by looking at the
\href{https://calendar.google.com/calendar/u/0/embed?src=rnboqiaki1k2la7rpu3bn0um58@group.calendar.google.com&ctz=America/Toronto}
{Google calendar} for the capstone course.}
\fi
\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Omar & 0\\
Daniel & 1\\
Andrew & 0\\
Olivia & 0\\
Khalid & 0\\
\bottomrule
\end{tabular}
\end{table}

We aim to always have at least one team member present to take notes, who is then responsible for keeping the team informed.

\section{TA Document Discussion Attendance}
\iffalse
\wss{For each team member how many of the informal document discussion meetings
with the TA were attended over the time period of interest.}
\fi
\noindent \textbf{TA's Name: } [Chris Schankula]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Omar & 1\\
Daniel & 1\\
Andrew & 0\\
Olivia & 1\\
Khalid & 0\\
\bottomrule
\end{tabular}
\end{table}

Unfortunately for this final TA Meeting, two team members had other commitments that could not be rescheduled.

\section{Commits}
\iffalse
\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}
\fi
\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 79 & 100\% \\
Omar & 2 & 2.6\% \\
Daniel & 28 & 35.4\% \\
Andrew & 12 & 15.2\% \\
Olivia & 29 & 36.7\% \\
Khalid & 8 & 10.1\% \\
\bottomrule
\end{tabular}
\end{table}

As discussed in previous reports, differences in commits is due to some team members commiting larger sections at once.

\section{Issue Tracker}
\iffalse
\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}
\fi
\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Omar & 0 & 0 \\
Daniel & 37 & 5 \\
Andrew & 0 & 0 \\
Olivia & 9 & 10 \\
Khalid & 0 & 5 \\
\bottomrule
\end{tabular}
\end{table}

Within this time period, not only were many issues created as bugs were identified; issues were not created for testing, 
hence why some team members have an odd issue closed/authored ratio based on their responsibility. Additionally as in previous
reports, team members forget to link issues until after the fact, and some issues deal with tracking meetings.

\section{Team Charter Trigger Items}

The triggers for team performance and accountability are as follows:

\begin{itemize}
    \item \textbf{Meeting Frequency:} Team meetings must be held at least once per week, with all members expected to attend unless otherwise specified.
    \item \textbf{Supervisor Updates:} The supervisor must be updated at least once every two weeks via email, unless questions arise that require more frequent communication.
    \item \textbf{Code Review Requirements:} Each pull request must be reviewed by at least two other team members before being merged into the main branch.
    \item \textbf{Performance Metrics:} Team member contributions are tracked using commits, meetings attended, and issues completed to evaluate performance.
    \item \textbf{Underperformance Criteria:} A team member is considered underperforming if they are not contributing to the project or are not meeting deadlines, which triggers a team meeting to address the issue.
\end{itemize}

Our team has experienced no violations of these triggers in the team charter.

\section{Additional Productivity Metrics}

Our team has no other productivity metrics in use.

\end{document}