\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{amsmath}


\title{Problem Statement and Goals\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Sept. 16, 2025 & Khalid Farag & Extras\\
Sept. 18, 2025 & Omar Abdelhamid & Problem Statement, Goals, Stretch Goals\\
Sept 20, 2025 & Khalid Farag & Group and Personal Reflection\\
Sept. 21st, 2025 & All & Personal Reflections\\
April 2nd, 2026 & All & Final Changes to Problem Statement, Goals, Stretch Goals\\
\bottomrule
\end{tabularx}
\end{table}

\section{Problem Statement}
The following subsections detail the project's overall problem statement, its inputs and outputs in terms of 
files and/or interactions, major stakeholders, and the environment the project will exist within (e.g. 
software platform).

\subsection{Problem}
There is currently no software that allows users to both design 3D models and automatically voxelize them into cubic units with support for assigning specific magnetization metadata to each voxel. As a result, current graduate students working with magnetic 3D printers are forced to construct the voxelized structures for their magnetic micro-robots manually. Given the small size of each voxel, models can consist of hundreds or thousands of voxels, each requiring individual creation and metadata assignment. This results in a slow, time-consuming, and inefficient workflow that limits productivity. As a result, graduate students are unable to focus on design iteration and experimentation and must instead spend significant time on manual construction of magnetic micro-robot systems.

\subsection{Inputs and Outputs}
\textbf{Inputs}
\begin{itemize}
  \item Finished 3D designs exported from standard CAD tools (e.g., STL/OBJ files from AutoCAD).
  \item Researcher-defined property specifications (e.g., material type, magnetization) for particular spatial regions of the design.
\end{itemize}

\noindent\textbf{Outputs}
\begin{itemize}
  \item Per-voxel property data (location, layer index, and associated properties) in a format consumable by the custom printer pipeline.
\end{itemize}


\subsection{Stakeholders}

In this section, we identify the stakeholders of the project, their roles and interests in the project. These stakeholders hold the most influence over the project, and their input is crucial for the success of the project.

\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Stakeholder} & \textbf{Role / Interest}\\
\midrule
Researchers / Engineers & Primary users who design and print multi-material objects; need fast, reliable voxel-level property assignment after design creation.\\
Lab Operators / Printer Owners & Consume the exported file to run the custom printer workflow; care about correctness and repeatability.\\
Supervisors / PIs (Approvers) & Validate that assigned properties are correct for the experiment’s goals.\\
\bottomrule
\end{tabularx}
\subsection{Environment}

This section details the environment in which the project will exist. This includes the platforms, runtime/integration, and assumptions about the environment.
\begin{itemize}
  \item \textbf{Platforms:} Desktop/laptop; Windows with WSL or native Linux.
  \item \textbf{Runtime/Integration:} Reads mesh CAD files for voxelization; exports a Java-readable file to drive a custom printer program.
  \item \textbf{Assumptions:} Commodity hardware (laptop/desktop) sufficient for interactive layer viewing and voxel selection.
\end{itemize}



\section{Goals}
This section details the high-level goals of the project. Our ultimate goal is to improve the current workflow and systems being used by grad students in order to create the models for their 3D-printed magnetic micro robots. This goal will be achieved through the following aspects of the system:

\begin{enumerate}
  \item \textbf{Import:} The system enables the import of mesh CAD files (STL) to decouple automated voxelization and metadata property assignment from the 3D model creation process. This allows users to leverage industry-standard CAD tools by designing models in external software.
  \item \textbf{Voxelization Algorithm:} The system automates the process of voxelizing a mesh CAD file to eliminate the need for manual, voxel-by-voxel construction of structures and significantly reduce the time required to create complex models.
  \item \textbf{Layered UI \& Selection:} The system provides simple and intuitive layer-based navigation, enabling users to efficiently access and interact with voxels throughout the entire structure.
  \item \textbf{Property Assignment \& Editing:} The system enables efficient assignment and modification of material and magnetization properties, allowing precise customization of voxel metadata for the 3D printing process.
  \item \textbf{Export:} The system supports exporting all necessary voxel data in a format compatible with the software that controls the 3D printing process, ensuring seamless integration with the existing 3D printer system.

\end{enumerate}

\section{Stretch Goals}
This section lists some stretch goals for the project that may be considered if time permits, or if the 
project continues past initial schedule.

\begin{itemize}
  \item \textbf{Adjustable Voxel Size:} Make voxel dimensions configurable to match different printers (beyond the fixed initial values).
  \item \textbf{Solid CAD Ingest (Future):} Add support for solid CAD (e.g., STEP/IGES) with robust tessellation before voxelization.
  \item \textbf{Additional Export Formats:} Support exporting to formats beyond the Java-based output to integrate with other software/hardware.
\end{itemize}

\section{Extras}

The extras for this project are:

\begin{itemize}
    \item \textbf{User Manual}: This manual will provide a comprehensive guide and explanations on how to effectively use the software, emphasizing the key features that differentiate it from a normal CAD software. This is useful for helping users to operate the system independently, reducing the need for direct support, and ensuring they can utilize the system to its full potential with all of the features. To make it more user-friendly, the manual will be written in a way that is easy to understand and follow, with clear instructions and examples. It will also include any safety warnings that are relevant to the software.
    \item \textbf{Usability Report}: This report will document the findings from usability testing, including identified pain points, user feedback, and recommendations from stakeholders for improving the user experience. It will also include information about how the testing was held, including the number of participants, the tasks they were given, the questions they were asked, and its initial results. This is useful for ensuring the product is intuitive, efficient, and satisfying for its target audience, leading to higher user adoption and satisfaction.
\end{itemize}
\newpage{}

\section*{Appendix --- Reflection}

\iffalse
\wss{Not required for CAS 741}
\fi

\input{../Reflection.tex}

\subsection*{1. What went well while writing this deliverable?}
We were able to write the problem statement and goals in timely and efficient manner due to our ability to effectively gather and apply guidance from the supervisor. The meeting held with the supervisor helped us to clarify the project's scope and goals, and to ensure that we were on the right track. This ensured that the both our team and the supervisor were on the same page, in terms of the project's requirements and expectations. Having this clear understanding early on reduced any ambiguity or confusion, allowing us to focus on the actual implementation of the project.

\subsection*{2. What pain points did you experience during this deliverable, and how did you resolve them?}
\bigskip
\textbf{Khalid:} The pain point I experienced was the time it took to select a project for the capstone. It was difficult to find a project that was both interesting and challenging, and that would be a good fit for our team. Therefore it reduced the amount of time we had to work on this document. To overcome this, the meeting with the supervisor helped us to clarify the project's scope and goals, and I was able to prioritize the work on this document.
\newline
\newline
\textbf{Daniel:} One pain point I experienced was in identifying possible risks for the project's future. It required a lot of forward thinking, estimating where things could go wrong based on my current understanding of the work our group was taking on. Ultimately, by looking into exactly what we would want to demonstrate as a proof of concept, I was able to generate possible routes of failure as well as steps we would take in case any of these possibilities becomes reality.
\newline
\newline
\textbf{Andrew:} The pain point I experienced during this deliverable was some merge conflicts for latex compiled pdfs. It was very frustrating having to do git magic to fix it, and I even gave up at one point and deleted my branch to fix it. A way to fix this, instead of just adding it to gitignore would be ideal. 
\newline
\newline
\textbf{Olivia:} Overall, one of the major challenges was navigating the scope of this project. The size and undertaking of this project are very daunting when I compare it to the project I’ve done in the past. Therefore, I found it difficult during this milestone to determine where to start in defining this project and how to make a plan that encapsulates all that will be required, both in technical skills as well as group collaboration. To resolve this challenge, our group took the necessary steps to understand where we stood as a group in both skills and desired team dynamics. We also took the time to properly explore different project options that we believed would be a good fit. This led to lots of debate and individual introspection before we were able to come together as a group to decide on the project. Even then, once we decided on a project, we had to have a meeting with our supervisor to gain a better understanding of the exact scope we were looking to take on with this project.
\newline
\newline
\textbf{Omar:}The pain point I experienced was the lack of initial understanding of the project requirements and scope. This made it difficult to define clear and achievable goals for the project. To resolve this, we scheduled a meeting with our supervisor to discuss the project in detail. This meeting helped us clarify the project's objectives, constraints, and expectations, allowing us to refine our goals and ensure they were aligned with the project's requirements. My other pain point was dealing with merge conflicts in LaTeX files. To resolve this, I coordinated with my team members to ensure that we were working on separate sections of the document and regularly communicated about changes to avoid overlapping edits. Also we maintained a clear version control strategy to manage contributions effectively while having a pull request review process to catch any potential conflicts early and we were in constant communication to ensure everyone was on the same page and able to help each other when needed.


\subsection*{3. How did you and your team adjust the scope of your goals to ensure they are suitable for a Capstone project (not overly ambitious but also of appropriate complexity for a senior design project)?}
The team did not need to adjust the scope of our goals as we were able to meet the requirements of the project. The meeting with the supervisor further clarified the project's scope and goals, and we were able to ensure that our goals were suitable for a Capstone project.

\end{document}